Towards Spherical Robots for Mobile Mapping in Human Made Environments\tnoteref{mytitlenote}

### 2021-07-12 Latex/rebuttal.txt

We clarified that the shell can enclose all sensor without requiring a 
number of points of connection as individual enclosing for all sensors
would. Further we added the requirement, that the shell is very 
durable.

@@

> 
> Reviewer 2: The authors have written a very interesting paper on the
> topic of mobile mapping with a spherical robot in human-made
> environments. In a rather slim paper and pleasantly concise form,
> they present their approach and show first results based on
> simulated and real measurement data. The reading flow is mostly
> pleasant and no irrelevant information is given. Conversely, the
> authors leave out important details in several places, which would
> be very helpful for the reader's understanding. In the following,
> there are several points for improvement and critical questions that
> should be taken into account by the authors. Due to the large number
> and the importance of central points, I recommend a major revision.
> 
> - A short outline at the end of the introduction is missing and
> would give the reader a better overview of the further content and
> should therefore be added.

We added a short outline, introducing you to the next sections.

> - In the entire article, no reference is made to the targeted or
> required accuracy potential with regard to the quality of the pose
> determination and the final point cloud, which in my view requires
> at least a rough classification.

The accuracy potential strongly depends on the motion profile and 
hardware being used, thus is not easy to generalize. Therefore it is 
still omitted.

@@

> - For the short state of the art of existing mobile systems, which
> is mainly based on the authors' own systems, in my opinion, at least
> the NavVis VLX system could be added, which in comparison is newer
> and as a human-operated system for mapping is one of the benchmarks.

We added the NavVis VLX as a reference in the state of the art section.

> - The authors mention unknown and dangerous environments as a
> possible field of application, in which the advantages of the
> spherical system should come into play. However, only one space
> application is mentioned as a specific example, which may be valid
> in itself, but does not fit the topic of the paper very
> well. Application scenarios should therefore be supplemented by
> terrestrial areas and in particular by human-made environments,
> which better motivate the future use and justification of such
> systems for the reader.

We added four more terrestrial, human-made environments as dangerous examples where a compact, spherical robot would really unfold its potential.

@@

> - Why is there no qualitative validation for the results of the real
> data in Section 6.2? A reference scan based on a terrestrial laser
> scanner would be a possibility or otherwise based on the flatness of
> known planes in the registered point cloud?

We couldn't access the rooms the dataset was acquired in for a terrestrial 
reference scan in the time given.

> - In the Conclusion, the parallelism and perpendicularity within the
> environment is mentioned again, although this did not play a role in
> the main part of the paper. Therefore, the question arises why do
> the planes have to be parallel or perpendicular at all and why is
> this mentioned at the beginning? This is not clear, since no
> additional constraints on this additional information have been
> introduced so far. There are also already other methods available
> that take this idea of geometric constraints for georeferencing into
> account.

We removed the initial mention of parallelism and perpendicularity of the planes
as it is of no further interest in the rest of the manuscript.

@@

> Page 6, Figure 1: How are these values to be interpreted and from
> where are they derived? This is unclear.

We have specified this. It is chosen to still allow plane detection.

> Page 8, Column 1, Table 1: What is missing is a classification of
> the values in relation to the expectations / demands...which are,
> however, still missing in advance

This table was given to quantify the improvement of the map via the algorithm.
In particular they are put forward as evidence of the improvement.

@@

> Page 8, Column 1, Line 37-43: At this point, an interpretation of
> the significant second peak in the right-hand diagram in Figure 4
> should be made. This has not been discussed so far.

We redid the experiment with a larger amount of points (all that have
a point-to-point distance of less than 3000 cm). The second significant
peak was a artifact of the previous thresholding and hence is now not 
significant anymore.

> Page 8, Column 1, Line 51: "ten scans" means ten individual scan
> lines or 10 epochs or is this identical? What kind of temporal
> offset is there in between and wouldn't a motion model have to be
> taken into account for this or is an identical pose assumed for the
> ten scans?

We have specified which scans and that we assume constant pose.

### 2021-07-12 Latex/rebuttal.txt

> 
> Reviewer 2: The authors have written a very interesting paper on the
> topic of mobile mapping with a spherical robot in human-made
> environments. In a rather slim paper and pleasantly concise form,
> they present their approach and show first results based on
> simulated and real measurement data. The reading flow is mostly
> pleasant and no irrelevant information is given. Conversely, the
> authors leave out important details in several places, which would
> be very helpful for the reader's understanding. In the following,
> there are several points for improvement and critical questions that
> should be taken into account by the authors. Due to the large number
> and the importance of central points, I recommend a major revision.
> 
> - A short outline at the end of the introduction is missing and
> would give the reader a better overview of the further content and
> should therefore be added.

We added a short outline, introducing you to the next sections.

> - In the entire article, no reference is made to the targeted or
> required accuracy potential with regard to the quality of the pose
> determination and the final point cloud, which in my view requires
> at least a rough classification.

Unfortunatley we could not extract a 'ground trouth' scan for the real world datasets, due to covid pandemic issues. Both rooms were inaccessible, thus we evaluate the accuracy of the real world dataset on a later point in time.

@@

> Page 3, Column 1, Line 34-35: But what demands are made on the
> assignment? This is unclear to the reader, also in connection with
> the general quality requirements of the whole approach.

We have added a specification for "good enough for plane detection".

> Page 3, Column 1, Line 38: How can the threshold value be specified,
> since it is probably not identical for all applications and
> environments? Later, there is also no indication of the choice of
> the value in the own simulated and real data sets.

We indicated that we observed the noise level around the expected planes by the naked eye, as an educated guess. You find that part in the 'Local Planar Clustering' section.

### 2021-07-12 Latex/sections/registration.tex
sequential iteration added + results
Small fixes. TODO ANDREAS/DORIT

For the plane extraction the linescans need to be transformed into the project coordinate system.
Various pre-registration methods are suitable for this.
The most simple method is to use the data from an intertial measurement unit for a coarse alignment.
Alternative solutions combine multiple linescans into a metascan and perform registration methods known from terrestrial laser scanning \todo{add source here} or use a small number of iterations of continuous-time SLAM approaches such as the one presented in~\cite{REMSEN2013}.
This yields maps that can be used for plane registration and hence a point-to-plane correspondences based registration.

@@

Point-to-Plane correspondences are now established.
The distance models (Hesse and PPD) are utilized to check whether a cluster overlaps with any of the global planes, i.e. any point in the cluster has a Hesse distance smaller than some threshold $\epsilon_H$ and a PPD smaller than some additional threshold $\epsilon_P$, to the global plane.
For each overlap, we find the smallest angle between the corresponding cluster normal and the global plane normal, according to eq. \ref{eq:alphahat}.
Finally, a correspondence is established between all points in the cluster and the global plane, if the minimum angle between their normals is smaller than $\epsilon_\alpha$.

@@

\subsection{Further Optimizations of the Algorithm}

@@

Secondly, we employ a continuous iteration, where the scans are processed sequentially. 
This is especially useful for mobile systems, where pose errors accumulate due to increasing tracking uncertainties.
The assumption is that the error in one scan is also present in the following scan, plus some unknown new error.
We eliminate the error from scan $m$ which is also present in scan $m+1$ by applying the pose change from scan $m$, $\vec{\Pi}_{n,m} - \vec{\Pi}_{0,m}$ after $n$ gradient descent iterations, to scan $m+1$, before restarting gradient descent.

>>>>

For the plane extraction the linescans need to be transformed into the project coordinate system.
Various pre-registration methods are suitable for this.
The most simple method is to use the data from an intertial measurement unit for a coarse alignment.
Alternative solutions combine multiple linescans into a metascan and perform registration methods known from terrestrial laser scanning or use a small number of iterations of continuous-time SLAM approaches such as the one presented in~\cite{REMSEN2013}.
This yields maps that can be used for plane registration and hence a point-to-plane correspondences based registration.

@@

Point-to-Plane correspondences are now established.
The distance models (Hesse and PPD) are utilized to check whether a cluster overlaps with any of the global planes, i.e. any point in the cluster has a Hesse distance smaller than some threshold $\epsilon_H$ and a PPD smaller than some additional threshold $\epsilon_P$, to the global plane.
We observe the noise level around the expected planes by the naked eye. 
Then we set the thresholds accordingly. 
For each overlap, we find the smallest angle between the corresponding cluster normal and the global plane normal, according to eq. \ref{eq:alphahat}.
Finally, a correspondence is established between all points in the cluster and the global plane, if the minimum angle between their normals is smaller than $\epsilon_\alpha$.

@@

\subsection{Further Optimizations of the Algorithm}
\label{ssec:furtheropts}

@@

Secondly, we employ a sequential iteration, where the scans are processed one after another. 
This is especially useful for mobile systems, where pose errors accumulate due to increasing tracking uncertainties.
The assumption is that the error in one scan is also present in the following scan, plus some unknown new error.
We eliminate the error from scan $m$ which is also present in scan $m+1$ by applying the pose change from scan $m$, $\vec{\Pi}_{n,m} - \vec{\Pi}_{0,m}$ after $n$ gradient descent iterations, to scan $m+1$, before restarting gradient descent.
